MSB104_assignment1

### 2023-10-05 MSB104_assignment1.qmd
Commit 05.10.23
Update with GINIdata 05.10.23

```{r}
#| label: setup
#| output: false
#| message: false
#| echo: false
library(eurostat)
library(dineq)
library(tidyverse)
library(gridExtra)
library(modelr)
library(grid)
library(ggplotify)
library(vtable)
library(dplyr)
```

@@

>>>>

```{r}
#| label: setup
#| output: false
#| message: false
#| echo: false
library(eurostat)
library(dineq)
library(tidyverse)
library(gridExtra)
library(modelr)
library(grid)
library(ggplotify)
library(vtable)
library(dplyr)
library(dineq)
```

@@

# **GDP per Capita Calculation**

```{r}
# Merging data
merged_data <- merge(DE_FI_RO_pop, DE_FI_RO_gdp) 
```

```{r}
merged_data <- merged_data |> 
  mutate(GDP_per_capita = GDP/Population)
```

```{r}
summary(merged_data)
```

GINI

```{r}
merged_data <- merged_data %>%
  mutate(id_nuts2 = substr(Sub_regions,1,4))
#Gen Nuts 2 id
merged_temp <- merged_data %>%
group_by(id_nuts2, Year) %>%
mutate(gini_n2 = gini.wtd(GDP, Population)*100000) %>%
  ungroup()
```

```{r}
data <- data %>%
  mutate_(id_nuts3 = geo,
          id_nuts2 = substr(geo, 1,4),
          id_nuts0 = substr(geo, 1,2)
```

```{r}
#gen weighted gini
#for all
w.cv(data$gdp)
```
